The Ingestion layer uses the \texttt{LLVMLite} Python binding to parse program structure from LLVM IR in pre-compiled \texttt{.ll} files.

\begin{itemize}
    \item \textbf{\texttt{llvm\_events.py}:} Parses an IR module and emits a~\texttt{Program\-Event\-Stream}---a typed sequence of~\texttt{IR\-Event} records. Each event carries the function name, block name, opcode, full instruction text, its index within the function, debug line number, operand list, and a~classified \texttt{Event\-Kind}. Table~\ref{tab:eventkind_mapping} shows the opcode-to-\texttt{Event\-Kind} classification rules. Typed CFG edges are extracted directly from \texttt{LLVMLite} terminator operands (\texttt{br}, \texttt{switch}, \texttt{invoke}, \texttt{indirectbr}, \texttt{callbr}) with true/false labels on conditional branches.

\begin{table}[h]
\centering
\caption{Opcode-to-\texttt{EventKind} classification in \texttt{llvm\_events.py}.}
\label{tab:eventkind_mapping}
\renewcommand{\arraystretch}{1.3}
\rowcolors{2}{white}{gray!10}
\begin{tabularx}{0.9\columnwidth}{|X|c|}
\hline
\rowcolor[HTML]{4472C4}
\hline
\textcolor{white}{\textbf{LLVM IR Opcode(s)}} & \textcolor{white}{\textbf{EventKind}} \\ \hline
\texttt{alloca}                              & \texttt{alloca}  \\ \hline
\texttt{load}                                & \texttt{load}    \\ \hline
\texttt{store}                               & \texttt{store}   \\ \hline
\texttt{add, sub, mul, div}, etc.            & \texttt{binop}   \\ \hline
\texttt{icmp}, \texttt{fcmp}                 & \texttt{compare} \\ \hline
\texttt{call}                                & \texttt{call}    \\ \hline
\texttt{ret}                                 & \texttt{ret}     \\ \hline
\texttt{br}                                  & \texttt{br}      \\ \hline
all others                                   & \texttt{other}   \\ \hline
\end{tabularx}
\end{table}

    \needspace{3\baselineskip}
    \item \textbf{\texttt{cfg\_edge\_io.py}:} Serializes and deserializes \texttt{CFG\-Edge} lists to~JSON, enabling round-trip import/export of control-flow edges via dedicated CLI flags.

    \item \textbf{\texttt{analysis\_metadata\_io.py}:} Loads and saves dominator-tree and loop-analysis metadata as~JSON, supporting round-trip import and export via CLI flags.

    \item \textbf{\texttt{trace\_io.py}:} Reads and writes runtime path traces as JSON (\texttt{-{}-import-trace} / \texttt{-{}-export-trace}), used for overlay visualization in CFG traversal animations.

    \item \textbf{\texttt{dot\_layout.py}:} Parses a Graphviz DOT file produced by \texttt{opt -passes=dot-cfg} and computes a \texttt{Dot\-Layout} with node positions and edge routes for the CFG animation scene.

    \item \textbf{\texttt{display\_lines.py}:} Cleans raw IR text into per-function line lists used by the rich animation panels.
\end{itemize}
